Word learning at the semantics pragmatics interface

### 2020-04-01 paper/supplementary_material.Rmd
play around with visuals

The main purpose of the study was to study *how* children integrate different information sources during word learning and how this process develops with age. To do so, we use Bayesian cognitive models of pragmatic reasoning. We first describe an *integration model* which we think best represents the inference and integration processes and then specify how this model captures developmental change. Next, we ask how well this model *predicts* how children integrate the two information sources. That is, in a situation in which we know the development trajectories for the mutual exclusivity inference as well as for the common ground inference, what can we say about what happens when common ground and mutual exclusivity are combined. We then test the predictive power of the model by comparing the model predictions to the data from experiment 3. We use formal model comparison methods to test the *integration model* against a range of alternative models.

Finally, we ask how well our model *explains* the way that children integrate the two information sources. For this analysis, we fit the free parameters in the model to all the available data, those from experiment 1 and 2 as well as the integration data from experiment 3. We then compare the model to a range of alternative models that make different assumptions about how information is integrated and how this process develops. This approach answers the question of how we can best explain how children integrate the different information sources.

>>>>

The main purpose of the study was to study *how* children integrate different information sources during word learning and how this process develops with age. To do so, we use Bayesian cognitive models of pragmatic reasoning. We first describe an *integration model* which we think best represents the inference and integration processes and then specify how this model captures developmental change. Next, we ask how well this model *predicts* how children integrate information. That is, in a situation in which we know the development trajectories for the mutual exclusivity inference (for a particualr familiar object) as well as for the common ground inference, what can we say about what happens when they are combined. We then test the predictive power of the model by comparing the model predictions to the data from experiment 3. We use formal model comparison methods to test the *integration model* against a range of alternative models.

Finally, we ask how well our model *explains* the way that children integrate the different information sources. For this analysis, we fit the free parameters in the model to all the available data, those from experiment 1 and 2 as well as the integration data from experiment 3. We then compare the model to a range of alternative models that make different assumptions about how information is integrated and how this process develops. This approach answers the question of how we can best explain how children integrate the different information sources.
